The Impact of Malaria Episodes and Treatment Regimens on Adverse Pregnancy Outcomes in Ugandan Women

### 2025-03-30 products/manuscript/Manuscript.qmd
Update2

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.show="hold"}
# Load Required Libraries
# Essential libraries for data handling, visualization, and analysis

library(here)             # Manage file paths
library(tidyverse)        # Core data wrangling: includes dplyr, ggplot2, readr, forcats, lubridate
library(janitor)          # Cleaning column names
library(skimr)            # Quick data summary
library(gtsummary)        # Creating summary tables
library(gt)               # Formatting tables
library(knitr)            # Table formatting
library(kableExtra)       # Additional table customization
library(ggpubr)           # Publication-ready plots
library(Amelia)           # Missing data visualization
library(pwr)              # Power analysis
library(DiagrammeR)       # Flowcharts/Diagrams
library(survival)         # Survival analysis
library(survminer)        # Survival plots
library(flextable)
library(webshot2)
```

@@

*Table 3: Association Between Malaria Episodes and Risk of Stillbirth*
```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.show="hold"}
# Run parsimonious stillbirth model
model_stillbirth_pars <- logistf(
  stillbirth_bin ~ total_malaria_episodes_during_pregnancy +
    age_at_enrollment_years + gravidity + parity +
    hypertension + diabetes_mellitus,
  data = promo_data_clean
)

@@

# Map raw variable names to clean, reader‐friendly labels
variable_labels <- c(
  "total_malaria_episodes_during_pregnancy" = "Total malaria episodes during pregnancy",
  "age_at_enrollment_years" = "Age at enrollment (years)",
  "gravidity" = "Gravidity",
  "parity" = "Parity",
  "hypertensionYes" = "Hypertension",
  "diabetes_mellitusYes" = "Diabetes mellitus"
)

# Replace raw names with neat labels; replace any NA with blank
table_stillbirth_pars$Variable <- variable_labels[table_stillbirth_pars$Variable]
table_stillbirth_pars$Variable[is.na(table_stillbirth_pars$Variable)] <- ""

# Remove any row names so only the column appears in the final table
rownames(table_stillbirth_pars) <- NULL

# Display table with consistent styling using kable with format "pandoc"
kable(
  table_stillbirth_pars,
  format = "pandoc",
  caption = "*Table 3: Association Between Malaria Episodes and Risk of Stillbirth*",
  col.names = c("Exposure and Adjustment Variables", "Adjusted Odds Ratio (aOR)", "95% CI Lower", "95% CI Upper", "p-value")
) %>%
  kable_styling(full_width = FALSE, position = "center")

>>>>

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.show="hold"}
# Load Required Libraries for Data Handling, Visualization, and Analysis

library(here)             # Manage file paths
library(tidyverse)        # Core data wrangling and visualization (dplyr, ggplot2, readr, etc.)
library(janitor)          # Clean and format column names
library(skimr)            # Quick data summaries
library(gtsummary)        # Create summary tables
library(gt)               # Format tables
library(knitr)            # R Markdown table formatting
library(kableExtra)       # Enhanced table customization for kable output
library(ggpubr)           # Publication-ready plots
library(Amelia)           # Visualize missing data
library(pwr)              # Perform power analyses
library(DiagrammeR)       # Create flowcharts and diagrams
library(survival)         # Survival analysis functions
library(survminer)        # Visualize survival analysis results
library(flextable)        # Create tables for Word output
library(webshot2)         # Capture screenshots for HTML widgets in non-HTML outputs
library(logistf)          # Penalized logistic regression (Firth’s method)

@@

*Table 3: Association Between Malaria Episodes and Risk of Stillbirth*
```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.show="hold"}
# Ensure the logistf package is loaded
library(logistf)

# Optional: Check that required variables exist in the dataset
required_vars <- c("stillbirth_bin", "total_malaria_episodes_during_pregnancy", 
                   "age_at_enrollment_years", "gravidity", "parity", 
                   "hypertension", "diabetes_mellitus")
if(!all(required_vars %in% names(promo_data_clean))) {
  missing_vars <- required_vars[!required_vars %in% names(promo_data_clean)]
  stop("The following required variables are missing in promo_data_clean: ", paste(missing_vars, collapse=", "))
}

# Run parsimonious stillbirth model
model_stillbirth_pars <- logistf::logistf(
  stillbirth_bin ~ total_malaria_episodes_during_pregnancy +
    age_at_enrollment_years + gravidity + parity +
    hypertension + diabetes_mellitus,
  data = promo_data_clean
)

@@

# Map raw variable names to clean, reader-friendly labels
variable_labels <- c(
  "total_malaria_episodes_during_pregnancy" = "Total malaria episodes during pregnancy",
  "age_at_enrollment_years" = "Age at enrollment (years)",
  "gravidity" = "Gravidity",
  "parity" = "Parity",
  "hypertensionYes" = "Hypertension",
  "diabetes_mellitusYes" = "Diabetes mellitus"
)

# Replace raw names with neat labels; replace any NA (i.e., unmapped) with blank
table_stillbirth_pars$Variable <- variable_labels[table_stillbirth_pars$Variable]
table_stillbirth_pars$Variable[is.na(table_stillbirth_pars$Variable)] <- ""
rownames(table_stillbirth_pars) <- NULL

# Display table using kable with pandoc format
kable(
  table_stillbirth_pars,
  format = "pandoc",
  caption = "*Table 3: Association Between Malaria Episodes and Risk of Stillbirth*",
  col.names = c("Exposure and Adjustment Variables", "Adjusted Odds Ratio (aOR)", "95% CI Lower", "95% CI Upper", "p-value")
) %>%
  kable_styling(full_width = FALSE, position = "center")
